The shape of kelp: environmental influences on kelp morphology

### 2018-10-16 chapter_2.Rmd
moved map to intro as suggested. paragraph added

Due to the Cape Peninsula’s temperate latitude, winter months bring an increased frequency of frontal depressions that originate from the Southern Ocean [@Reason2006]. These low pressures are joined by large swells with increased wave energy. The nearshore environment, with the accompanied biota, therefore experiences high wave energy events, with increased frequency in winter. The large peninsula acts as an obstruction for large south westerly swells, providing decreased wave energy along the west side of False Bay [@Shipley1964]. Conversely, the west coast of Cape Point is battered by these large swells at full force. Multiple sites, therefore, exist where kelps grow in diverse temperature and wave energy climates, in close proximity.

>>>>

Due to the Cape Peninsula’s temperate latitude, winter months bring an increased frequency of frontal depressions that originate from the Southern Ocean [@Reason2006]. These low pressures are joined by large swells with increased wave energy. The nearshore environment, with the accompanied biota, therefore experiences high wave energy events, with increased frequency in winter [@Veitch2018]. The large peninsula acts as an obstruction for large south westerly swells, providing decreased wave energy along the west side of False Bay [@Shipley1964]. Conversely, the west coast of Cape Point is battered by these large swells at full force. Multiple sites, therefore, exist where kelps grow in diverse temperature and wave energy climates, in close proximity.

In Figure 1 the total and seasonal wave roses of the directional wave buoy just offshore from Cape Town is given form the years 2000 till end 2017 (the period for which directional wave spectra was available). It is due to the near consistent South-westerly swell waves and the complex orography around the peninsula, that the wave energy distribution around the Cape Peninsula varies significantly over a small geographical area. For details on the seasonality of the wave climate around the Cape peninsula please refer to [@Veitch2018].

**insert wave rider images here**
